---
title: "ML_2_Summary"
author: "Study Crew"
date: "3/9/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Machine Learning 2 Summary Document

This document is a comprehensive summary for Machine Learning 2. It is intended to help us study for the exams and for future reference in our professional lives (if any companies actually use R).


## Forward and Backward Selection
Author: Matt Sadosuk

### Summary/description:


### When to employ this method/model:



### Model Code and Inputs:

```{r}

```

### Model Tests:

```{r}

```

### Model Improvements:

```{r}

```

### Comprehensive Example:

```{r}

```
--------------------------------------------------------------------------------


## Ridge Regression
Author: Sarah Brown

### Summary/description:


### When to employ this method/model:



### Model Code and Inputs:

```{r}

```

### Model Tests:

```{r}

```

### Model Improvements:

```{r}

```

### Comprehensive Example:

```{r}

```
--------------------------------------------------------------------------------


## Lasso Regression
Author: Jill Van den Dungen 

### Summary/description:


### When to employ this method/model:



### Model Code and Inputs:

```{r}

```

### Model Tests:

```{r}

```

### Model Improvements:

```{r}

```

### Comprehensive Example:

```{r}

```
--------------------------------------------------------------------------------


## Principal Component Regression
Author: Alex King

### Summary/description:


### When to employ this method/model:



### Model Code and Inputs:

```{r}

```

### Model Tests:

```{r}

```

### Model Improvements:

```{r}

```

### Comprehensive Example:

```{r}

```
--------------------------------------------------------------------------------


## Polynomial Regression
Author: Carrington Metts

### Summary/description:


### When to employ this method/model:



### Model Code and Inputs:

```{r}

```

### Model Tests:

```{r}

```

### Model Improvements:

```{r}

```

### Comprehensive Example:

```{r}

```
--------------------------------------------------------------------------------


## Step Functions
Author: Alex Russett

### Summary/description:


### When to employ this method/model:



### Model Code and Inputs:

```{r}

```

### Model Tests:

```{r}

```

### Model Improvements:

```{r}

```

### Comprehensive Example:

```{r}

```
--------------------------------------------------------------------------------


## Regression Splines
Author: Andrew Tremblay & Thomas Trankle

### Summary/description:


### When to employ this method/model:



### Model Code and Inputs:

```{r}

```

### Model Tests:

```{r}

```

### Model Improvements:

```{r}

```

### Comprehensive Example:

```{r}

```
--------------------------------------------------------------------------------


## Smoothing Splines
Author: Emma Harrison

### Summary/description:


### When to employ this method/model:



### Model Code and Inputs:

```{r}

```

### Model Tests:

```{r}

```

### Model Improvements:

```{r}

```

### Comprehensive Example:

```{r}

```
--------------------------------------------------------------------------------


## Local Regression 
Author: Kayleigh Gillis

### Summary/description:


### When to employ this method/model:



### Model Code and Inputs:

```{r}

```

### Model Tests:

```{r}

```

### Model Improvements:

```{r}

```

### Comprehensive Example:

```{r}

```
--------------------------------------------------------------------------------


## GAM
Author: Akram Bijapuri

### Summary/description:


### When to employ this method/model:



### Model Code and Inputs:

```{r}

```

### Model Tests:

```{r}

```

### Model Improvements:

```{r}

```

### Comprehensive Example:

```{r}

```
--------------------------------------------------------------------------------


## Tree Classification and Regression 
Author: Ian Lawson 

### Summary/description:


### When to employ this method/model:



### Model Code and Inputs:

```{r}

```

### Model Tests:

```{r}

```

### Model Improvements:

```{r}

```

### Comprehensive Example:

```{r}

```
--------------------------------------------------------------------------------


## Bagging and Random Forest
Author: Witty Wittyngham

### Summary/description:


### When to employ this method/model:



### Model Code and Inputs:

```{r}

```

### Model Tests:

```{r}

```

### Model Improvements:

```{r}

```

### Comprehensive Example:

```{r}

```




